Eco-evolutionary dynamics of finite populations from first principles

### 2023-02-17 ind_files/06_unification_discussion.tex
Minor changes to discussion

\mathbb{E}\left[\frac{d\overline{\tau}}{dt}\right] = \underbrace{\vphantom{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right] } \mathbb{E}\left[\textrm{Var}(b^{\textrm{(ind)}}) - \textrm{Var}(d^{\textrm{(ind)}}\right]}_{\substack{\text{Classical selection} \\ \text{effects}}} \ - \ \underbrace{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right]}_{\substack{\text{Noise-induced selection} \\ \text{effects}}} \ + \ \underbrace{ \vphantom{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right] } \mathbb{E}\left[\hphantom{a}\overline{\hphantom{a}\frac{\partial \tau}{\partial t}\hphantom{a}}\hphantom{a}\right]}_{\substack{\text{Short-term (ecological)} \\ \text{feedbacks to $\tau_i$}}}

>>>>

\mathbb{E}\left[\frac{d\overline{\tau}}{dt}\right] = \underbrace{\vphantom{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right] } \mathbb{E}\left[\textrm{Var}(b^{\textrm{(ind)}}) - \textrm{Var}(d^{\textrm{(ind)}})\right]}_{\substack{\text{Classical selection} \\ \text{effects}}} \ - \ \underbrace{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right]}_{\substack{\text{Noise-induced selection} \\ \text{effects}}} \ + \ \underbrace{ \vphantom{ \mathbb{E}\left[\frac{\textrm{Var}(\tau)}{KN_K(t)}\right] } \mathbb{E}\left[\hphantom{a}\overline{\hphantom{a}\frac{\partial \tau}{\partial t}\hphantom{a}}\hphantom{a}\right]}_{\substack{\text{Short-term (ecological)} \\ \text{feedbacks to $\tau_i$}}}

### 2023-02-17 ind_files/99_Appendix_C.tex
Minor changes to discussion

Finally, we can now recognize that

@@

\textrm{Cov}\left(w, {\left(\overline{f}\right)}^2\right) &= \overline{\left(w{\left(\overline{f}\right)}^2\right)} - \overline{w}\overline{\left({\left(\overline{f}\right)}^2\right)}\\
&= {\left(\overline{f}\right)}^2\sum\limits_{i=1}^{m}w_ip_i - \overline{w}{\left(\overline{f}\right)}^2\sum\limits_{i=1}^{m}p_i\\

@@

\textrm{Cov}\left(\tau,f^2 - {\left(\overline{f}\right)}^2\right) &= \overline{\tau\left(f^2 - {\left(\overline{f}\right)}^2\right)} - \overline{\tau}\left(\overline{f^2 - {\left(\overline{f}\right)}^2}\right)\\
&= \overline{\tau f^2} - \overline{\tau}{\left(\overline{f}\right)}^2  - \overline{\tau}\overline{f^2} + \overline{\tau}{\left(\overline{f}\right)}^2\\

@@

@@

d\sigma^2_{f} &= \textrm{Cov}\left(w,(f - \overline{f})^2\right)dt\\[12pt]
&- \frac{1}{KN_K}\left[ \ 2\textrm{Cov}\left(\tau,(f - \overline{f})^2\right) + \overline{\tau}\sigma^2_{f}(t) \ \right]dt\\[12pt]

@@

>>>>

To simplify the covariance terms of the first line of the RHS, we observe that

@@

\textrm{Cov}\left(w, {\left(\overline{f}\right)}^2\right) &= \overline{\left(w{\left(\overline{f}\right)}^2\right)} - \overline{w}\overline{\left({\left(\overline{f}\right)}^2\right)}\nonumber\\
&= {\left(\overline{f}\right)}^2\sum\limits_{i=1}^{m}w_ip_i - \overline{w}{\left(\overline{f}\right)}^2\sum\limits_{i=1}^{m}p_i\nonumber\\

@@

\textrm{Cov}\left(\tau,f^2 - {\left(\overline{f}\right)}^2\right) &= \overline{\tau\left(f^2 - {\left(\overline{f}\right)}^2\right)} - \overline{\tau}\left(\overline{f^2 - {\left(\overline{f}\right)}^2}\right)\nonumber\\
&= \overline{\tau f^2} - \overline{\tau}{\left(\overline{f}\right)}^2  - \overline{\tau}\overline{f^2} + \overline{\tau}{\left(\overline{f}\right)}^2\nonumber\\

@@

\label{stochastic_Price_variance}

@@

d\sigma^2_{f} &= \textrm{Cov}\left(w,(f - \overline{f})^2\right)dt - \frac{1}{KN_K}\left[ \ 2\textrm{Cov}\left(\tau,(f - \overline{f})^2\right) + \overline{\tau}\sigma^2_{f}(t) \ \right]dt\\[12pt]

@@

In the case of one-dimensional quantitative traits, an infinite-dimensional version of \eqref{stochastic_Price_variance} has been rigorously derived \citep{week_white_2021} in a recent paper for the case where $f$ is the phenotypic value of the quantitative trait - Equation (21b) of \cite{week_white_2021} is precisely the $m \to \infty$ version of my equation \eqref{stochastic_Price_variance} when $f$ is the phenotypic value of the quantitative trait under consideration.
